\documentclass{book}
\author{Kyle Thomas}
\title{truthforce}

\begin{document}
\tableofcontents

\section{Truthforce}
Define truthforce to be that which grows a tree of accurately descriptive knowledge.
Truthforce is free of the bias of an author.
This freedom is the value afforded by the audience's verification of knowledge.

\section{Wisdom Maximized for Its Size}
\subsection{Aid in a Sentence}
Optimize behaviors to be the change you want to see in the World.

\subsection{Aid in a Paragraph}
Nourish a body with nuts, seeds, beans, greens, grains, fruits, vegetables, ferments, fungi, focus, and fasts.
Manage life to regularly include vigorous rather than strenuous exertion.
Meditate upon breath to practice focus upon breath's foundational exertion.
Let your body show you what needs attention.
Sometimes the solution is obvious and sometimes what seems obvious obscures a holistic solution.

\section{Access}
\subsection{Welcome to the Party}
The party gathers to converse about what we observe, how to predict the future, and how to drive our lives.

\subsection{Invitation to the Conversation}
There is a conversation in which math is a language used to communicate precisely in a very efficient manner.
Access to this conversation requires knowledge of math.
The knowledge which makes this conversation accessible is simple.

\subsection{Measurably Minute Math}
Math is a language that lives through us to become the platform upon which we can rigorously investigate, communicate, and confirm arbitrarily complicated concepts.
This language can integrate with other language to describe itself.
A survey of math can model topics as building upon each other as listed for the example of arithmetic.

\begin{enumerate}
	\item Multiplication is repeated additions.
	\item Exponentiation is multiplying repeated factors.
	\item Consult Euler's formula: \ref{eq:Euler's-formula}.
\end{enumerate}

\begin{equation}e^{i\theta}=\cos(\theta)+i\sin(\theta).\label{eq:Euler's-formula}\end{equation}

A general mathematical procedure is listed.

\begin{enumerate}
	\item Name known and unkown quantities.
	\item Order the numbers.
	\item Specify our certainty of known quantities.
	\item Create data structures to describe collections of numbers.
	\item Learn the standard arithmetic operations.
	\item Imagine a new dimension labeled by a newly imagined number for each kind of number to gain closure over the veracity of all relations of all operations.
	\item Relate quantities.
	\item Learn algebraic manipulations of related quantities.
	\item Calculate variations of related quantities with respect to one another.
	\item Name abstract functions that map between ordered sets of quantities.
	\item Characterize multitudes of data with statistics.
\end{enumerate}

\subsection{Language About Itself}
Language connects professors, students, and arbitrarily magnificent concepts.

\subsubsection{Exploring Definition}
\begin{itemize}
	\item enjoy: (transitive verb)bring into a state joy
	\item dumb: (adjective)without knowledge
	\item ignorance: (noun)independence of behavior; this behavior could be described as dumb to what is ignored because the behavior shows no evidence of awareness
\end{itemize}

\subsection{Known Concepts are a Living Language Named Science}

\section{Health}
\subsection{Managagement of Wealth as Holistic Health}
Holistic mangement of health can contain a recognition that happiness is a choice.
A continuously informed choice of happiness may be implemented as the entire management of health.
Distractions arise following mismanagement of health.
Management is focused by new management informed by health's response to management.

Arteriosclerotic plaque is an accreted deposit fixed within vasculature.
Mechanical cleaning is one mechanism of maintenance which can in principal be effected by changes in pressure, vasoconstriction, vasodilation, or general manipulation.
Changes in pressure can be accomplished by exercise.
Vasoconstriction and vasodilation accompany temperature change.
Vasculature is manipulated by exercise and massage.

\subsection{Diet}
Diet can be specified as eating events.
An event specifies what, how, and when food was consumed.
When food is eaten can be specified in a time-basis or frequency-basis.

A body is nourished when food is chosen, prepared, and eaten in a way that supplies nutrients in a bioavailable form.
Run an experiment of eating the same foods chewed with varied throroughness.
Optimize for health that supports the best feeling in the body.

Truthforce manifests itself as a compulsion to feed health once good food is felt.
Make food from these formulae to feel compelled to be healthy.
We eat to live: let us enjoy what we are thus defined to do professionally.

\begin{enumerate}
	\item Butter can be made from garlic, vegetables, nuts, seeds, cooked beans, and fermented grains.
	\item Many seeds are wonderful emulsifiers.
	\item Hummus can be made by blending
		\begin{enumerate} 
			\item 2 teaspoons(10mL) juice of lemon;
			\item 3 cloves garlic;
			\item 2 teaspoons(10mL) cumin;
			\item 2 teaspoons(10mL) seeds;
			\item 1 cup(240 mL) beans;
			\item aquafaba, which is the liquid the beans were prepared in, to liquify and thin as desired;
			\item oats to thicken and set as desired;
			\item celery and other herbs or spices to mineralize, emulsify, and flavor as desired.
		\end{enumerate}
	\item Fry by heating a pan at medium-high until water dances when dripped in the pan then adding food in order of how long it takes to cook, splashing around one tablespoon(30mL) of acidified water to deglaze ingredients as needed.
	\item Starches gelatinize at temperatures below boiling.
	\item Syneresis can occur 

\end{enumerate}

\subsection{Exercise}
Exercise is a proof of ability that builds itself.

\subsection{Water}
Water can limit feelings of wellbeing.
This is easily enough observed by considering limiting cases.
Getting no water permits no feeling of wellbeing.

\subsection{Sleep}
Sleep deprivation can be accompanied by paranoia in ways similar to a paranoid anxiety associated with marijuana's effects.
Studies in the literature suggest that sleep deprivation could be an intermediary cause of the anxiety some experience while using marijuana.

\subsection{Cancer}
Cancer seems to be advantageously modeled as an organism's adaptive growth in response to changes in stimuli.
\end{document}
